Does It Scale? Symbolic Execution of PHP Web Applications

### 2017-02-03 related.tex
revised version

\paragraph{Symbolic Execution}
An overview about recent evolution of symbolic execution is provided
by Cadar {\em et al.}~\cite{CadarSen2013}, as well as a more
tool-centered perspective~\cite{Cadar2011}.
%
Symbolic execution \cite{King1976,Darringer1978} remained a
conceptual approach for decades, but has been refined and extended
over the last years. Several approaches incorporating constraint
solving and leveraging concrete execution alongside symbolic execution
emerged and enable automated test case generation; the scalability of
these approaches is still challenged by path explosion and constraint
solving.

@@

Wang {\em et al.}~\cite{wang-fse12}'s approach executes the
(instrumented) server-side code with a specific input to generate the
client code. Changes in that generated code can then be mapped to
their origins in the PHP code using the recorded run-time mappings and
static impact analysis.
%We similarly track origin locations, but we symbolically execute the
%PHP code.
%
%We previously used our symbolic execution engine \emph{PhpSync} for
%similar purposes~\cite{drc-ase13,phpsync}. First, we 
PHPSync~\cite{phpsync} used our static origin tracking to propagate
changes in the client code (output of symbolic execution) back to the
PHP code. Subsequently, the same authors designed DRC to analyze both
PHP code and generated client-side code to detect cross-language and
cross-stage dangling references~\cite{drc-ase13}. DRC matches path
constraints of references/declarations without fully symbolic
execution. It uses the path conditions from symbolic execution to
determine in which configurations dangling references can occur.
%
%In contrast to this work, DRC extracts program entities 
%(identifiers)
%via heuristics:
%%and {\em is not} able to parse and understand the structure and
%%semantics of the embedded code; DRC
%it just matches path constraints of
%references/declarations without building the ASTs and DOM for embedded
%code in different configurations.
%%In the future, we plan to integrate DRC's analyses to derive
%%additional call-graph edges that cross languages and stages.

Apollo~\cite{artzi-icse10,artzi-tse10}, a more general fault
localization tool for PHP code, rates the PHP echo/print
statements higher in suspiciousness by running an instrumented
interpreter on test cases. Clark {\em et al.}~\cite{clark-ase11}
localize faults in an SQL command embedded within JSP code. Although
not in our focus, we could conceptually use our tool to approximate
embedded SQL queries and use a variability-aware SQL parser for
analysis.

%-------------------

%-------------------------------------

>>>>

\paragraph{Symbolic execution}
A literature review on symbolic execution is provided by Cadar in a
recent overview {\em et al.}~\cite{CadarSen2013}, as well as in a more
tool-centered perspective~\cite{Cadar2011}.
%
Symbolic execution \cite{King1976,Darringer1978} remained a
conceptual approach for decades, but has been refined and extended
over the last years. Several approaches incorporating constraint
solving and leveraging concrete execution alongside symbolic execution
emerged and enable automated test case generation; the scalability of
these approaches is still challenged by path explosion and constraint
solving.

@@

Wang {\em et al.}~\cite{wang-fse12}'s approach executes the
(instrumented) server-side code with a specific input to generate the
client code. Changes in that generated code can then be mapped to
their origins in the PHP code using the recorded run-time mappings and
static impact analysis.
%We similarly track origin locations, but we symbolically execute the
%PHP code.
%
%We previously used our symbolic execution engine \emph{PhpSync} for
%similar purposes~\cite{drc-ase13,phpsync}. First, we 
PHPSync~\cite{phpsync} used static origin tracking to propagate
changes in the client code (output of symbolic execution) back to the
PHP code. Subsequently, the same authors designed DRC to analyze both
PHP code and generated client-side code to detect cross-language and
cross-stage dangling references~\cite{drc-ase13}. DRC matches path
constraints of references/declarations without fully symbolic
execution. It uses the path conditions from symbolic execution to
determine in which configurations dangling references can occur.

Apollo~\cite{artzi-icse10,artzi-tse10}, a more general fault
localization tool for PHP code, rates the PHP echo/print
statements higher in suspiciousness by running an instrumented
interpreter on test cases. Clark {\em et al.}~\cite{clark-ase11}
localize faults in an SQL command embedded within JSP code.
